Tutorial_2b

### 2024-10-19 Tutorial_2b.Rmd
update tut2b

```{r save-plot-effects, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M4effects_con_incon_3trials.png", width = 8, height = 8, dpi = 300)
```

@@

```{r save-table-interval-estimates, eval=F}
write_csv(test, file="Tutorial_2_Bayesian/tables/effects_intervals_table.csv")
```

@@

```{r save-plot-fit-hazard, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M4effects_subject6.png", width = 10, height = 10, dpi = 300)
```

>>>>

```{r save-plot-effects, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M4_ca_effects_con_incon_3trials.png", width = 8, height = 8, dpi = 300)
```

@@

```{r save-table-interval-estimates, eval=F}
write_csv(test, file="Tutorial_2_Bayesian/tables/ca_effects_intervals_table.csv")
```

@@

```{r save-plot-fit-hazard, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M4_ca_effects_subject6.png", width = 10, height = 10, dpi = 300)
```
